No Title

### 2017-10-26 paper/paper.tex
inertia tensor

\begin{abstract}
We quantify the joint spatial distribution of the brightest satellites
around the Milky way and M31. 
We find that the satellites in MW show a distribution significantly
thinner and flattened compared to the expectaions of a random
spherical distribution and simulations based on the Lambda Cold Dark
Matter paradigm.
In turn, M31 is completely consistent with the expectations from a
spherical satellite distribution and LCDM simulations.
The satellite planes in the MW and M31 are almost perpendicular to the line
connecting the two galaxies. None of the pairs in the simulation show
a similar degree of alignment. 
However, the simulations are consistent with a random uniform
distribution, making the result from the observations consistent with
these theoretical expectations.
This special satellite distribution in the Milky Way makes the Local
Group an atypical pair in the expected cosmological context.
We summarize these results in a simple multivariate Gaussian
model to estimate that only $1\%$ of the pairs with isolation
and dynamical characteristics similar to the LG are expected to have
satellite distributions with the same degree of atipicality. 
\end{abstract}

@@

We base all our results on the description provide by the inertia
tensor defined by the satellites's positions.

\begin{equation}
{\bf{\bar{I}}} = \sum_{k \in V}[(\bf{r}_i - \bf{r}_0)^2\cdot \bf{1} -
  (\bf{r}_i-\bf{r}_0)\cdot (\bf{r}_i - \bf{r}_0)^{T}],
\end{equation}
%
where $k$ indexes the set of satellites of interest
$\bf{r}_k$ are the satellites' positions, $\bf{r}_{0}$ is the location
of the satelites's geometric center ${\bf r}_{0}\equiv \frac{1}{N_s}\sum_{k\in
  V} \bf{r}_i$, $\bf{1}$ is the unit matrix,  and  
${\bf r}^T$ is the transposed vector $\bf{r}$.

>>>>

\begin{abstract}
We quantify the joint spatial distribution of the brightest satellites
around the Milky way and M31. 
We find that the satellites in MW show a distribution significantly
thinner and flattened compared to the expectaions of a random
spherical distribution and simulations based on the Lambda Cold Dark
Matter paradigm.
In turn, M31 is completely consistent with the expectations from a
spherical satellite distribution and LCDM simulations.
The satellite planes in the MW and M31 are almost perpendicular to the line
connecting the two galaxies. None of the pairs in the simulation show
a similar degree of alignment. 
However, the simulations are consistent with a random uniform
distribution, making the result from the observations consistent with
these theoretical expectations.
This special satellite distribution in the Milky Way makes the Local
Group an atypical pair in the cosmological context provided by
simulations. 
We summarize these results in a simple multivariate Gaussian
model to estimate that only $1\%$ of the pairs with isolation
and dynamical characteristics similar to the LG are expected to have
satellite distributions with the same degree of atipicality. 
\end{abstract}

@@

We base all our results on the description provided by the inertia
tensor defined by the satellites's positions.

\begin{equation}
{\bf{\bar{I}}} = \sum_{k \in V}[(\bf{r}_i - \bf{r}_0)^2\cdot \bf{1} -
  (\bf{r}_i-\bf{r}_0)\cdot (\bf{r}_i - \bf{r}_0)^{T}],
\end{equation}
%
where $k$ indexes the set of satellites of interest
$\bf{r}_k$ are the satellites' positions, $\bf{r}_{0}$ is the location
of the central galaxy $\bf{1}$ is the unit matrix,  and  
${\bf r}^T$ is the transposed vector $\bf{r}$. 
We use $\bf{r}_0$ as the position of the central galaxy, and not the
satellites' geometrical center, to allow for a fair comparison once
the angular positions of the satellites are randomized around this
point.
